FoRTE baseline

### 2019-04-22 analysis/paper/paper.Rmd
Add parameter distributions to paper.Rmd

Plant functional type definitions:
- Early successional hardwood
    - _Betula papyrifera_ (white/paper birch)
    - _Populus grandidentata_ (bigtooth aspen)
    - ?? _Populus tremuloides_ (trembling aspen)
    - ?? _Prunus pensylvatica_ (fire cherry)
- Mid successional hardwood
    - _Quercus rubra_ (red oak)
    - _Acer rubrum_ (red maple)
    - ?? _Betula alleghaniensis_ (yellow birch)
    - ?? _Tilia americana_ (basswood)
    - ?? _Fraxinus americana_ (white ash)
- Late successional hardwood
    - _Acer saccharum_ (sugar maple)
    - _Fagus grandifolia_ (American beech)
    - ?? _Ostyra virginiana_ (hop-hornbeam)
    - ?? _Acer pensylvaticum_ (striped maple)
- Pine
    - _Pinus strobus_ (white pine)
    - ?? _Pinus resinosa_

@@

```{r annual_means, fig.cap = annual_means_cap, fig.dim = c(5, 7)}
readd(old_ensemble_plot)
```

>>>>

Plant functional type definitions:

- **Early successional hardwood**
    - _Betula papyrifera_ (white/paper birch)
    - _Populus grandidentata_ (bigtooth aspen)
    - ?? _Populus tremuloides_ (trembling aspen)
    - ?? _Prunus pensylvatica_ (fire cherry)
- **Mid successional hardwood**
    - _Quercus rubra_ (red oak)
    - _Acer rubrum_ (red maple)
    - ?? _Betula alleghaniensis_ (yellow birch)
    - ?? _Tilia americana_ (basswood)
    - ?? _Fraxinus americana_ (white ash)
- **Late successional hardwood**
    - _Acer saccharum_ (sugar maple)
    - _Fagus grandifolia_ (American beech)
    - ?? _Ostyra virginiana_ (hop-hornbeam)
    - ?? _Acer pensylvaticum_ (striped maple)
- **Pine**
    - _Pinus strobus_ (white pine)
    - ?? _Pinus resinosa_

```{r methods_captions}
param_dist_cap <- paste(
  "Input parameter distributions."
)
```

```{r param_dist, fig.cap = param_dist_cap, fig.dim = c(13, 10)}
readd(param_dist_gg)
```

@@

```{r annual_means, fig.cap = annual_means_cap, fig.dim = c(5, 7)}
## readd(old_ensemble_plot)
```
